### 2023-12-21 README.Rmd
Update README

# rang <img src="man/figures/rang_logo.svg" align="right" height="200" />

@@

```r
rang_rio <- resolve("rio", snapshot_date = "2013-08-28") ## R 3.0.1
dockerize(rang_rio, output_dir = "~/old_renviron")
```

>>>>

# rang <img src="man/figures/rang_logo.png" align="right" width = "120" />

@@

```r
rang_rio <- resolve("rio", snapshot_date = "2013-08-30") ## R 3.0.1
dockerize(rang_rio, output_dir = "~/old_renviron")
```

## `evercran` support (experimental)

`rang` supports [evercran](https://github.com/r-hub/evercran). As of writing, the support is still experimental (just like `evercran` itself). In the future, `evercran` will replace the Debian method.

```r
rang_rio <- resolve("rio", snapshot_date = "2013-08-30") ## R 3.0.1
dockerize(rang_rio, output_dir = "~/old_renviron", method = "evercran")
```
